(TEMP) Online Video Game Monetization Schemes and Its Relationship to the Consumers

### 2022-04-24 outputs/paper/paper.Rmd
Added more content to the Data section of paper.Rmd. Added preliminary model justifications in the Model section of paper.Rmd.

```{r setup, include=FALSE}
# Load required packages and read in the data
knitr::opts_chunk$set(echo = TRUE)

@@

cleaned_data <-
  read_csv(here::here("outputs/data/cleaned_data.csv"))
```

@@

Figure \@ref(fig:graph1) showcases this issue: For respondents who claimed
that having a VP active is crucial to their enjoyment of the game, only a few
reported having consistent success purchasing VPs from the central market.

```{r graph2, fig.cap="Rated Importance of Value Pack Versus Number of Value Packs Purchased on Central Market",  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Create a graph that showcases the importance of VP vs. number of VP bought
#   from the central market
# Row 6, 24 and 112 seem to be an outliers; no dicernable reason for someone to purchase
#   enough VPs for more than number of days the game has been released for.
#   Possible input error from the respondent. Regardless, removed for a more
#   visually clear graph
cleaned_data[-c(6,24,112),] |>
  ggplot(aes(x = importance_vp, y = cm_vp_count)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  theme_minimal() +
  labs(x = "Importance of Value Pack to one's Enjoyment of the Game",
       y = "Number of VPs Purchased on Central Market")

@@

@@

TODO

@@

TODO

@@

TODO

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
# Load required packages and read in the data
knitr::opts_chunk$set(echo = TRUE)

@@

# Variables of class factor must be mutated as such again
cleaned_data <-
  read_csv(here::here("outputs/data/cleaned_data.csv")) |>
  mutate(age_group = as.ordered(age_group)) |>
  mutate(gender = as.factor(gender)) |>
  mutate(character_total = as.ordered(character_total)) |>
  mutate(character_female = as.ordered(character_female)) |>
  mutate(gender_main = as.factor(gender_main)) |>
  mutate(package_free = as.factor(package_free))

# Organize the factor levels of character_female and character_total
cleaned_data <- cleaned_data |>
  mutate(character_female = ordered(character_female,
                                    levels = c("0","1","2","3","4","5","6",
                                               "7","8","9","10","10+"))) |>
  mutate(character_total = ordered(character_total,
                                    levels = c("0","1","2","3","4","5","6",
                                               "7","8","9","10","10+")))
```

@@

Figure \@ref(fig:graph1) showcases this issue: For respondents who claimed
that having a VP active is crucial to their enjoyment of the game, only a few
reported having consistent success purchasing VPs from the central market.
Because of this, respondents could be pressured into relying more 
on purchasing VPs through the pearl shop.

```{r graph2, fig.cap="Rated Importance of Value Pack Versus Number of Value Packs Purchased on Central Market",  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Create a graph that showcases the importance of VP vs. number of VP bought
#   from the central market
# Row 6, 24 and 112 seem to be outliers; no discernible reason for someone to purchase
#   enough VPs for more than number of days the game has been released for.
#   Possible input error from the respondent. Regardless, removed for a
#   visually clearer graph
cleaned_data[-c(6,24,112),] |>
  ggplot(aes(x = importance_vp, y = cm_vp_count)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  theme_minimal() +
  labs(x = "Importance of Value Pack to one's Enjoyment of the Game",
       y = "Number of VPs Purchased on Central Market")

@@

This line of thinking is echoed by the observations in Table \@ref(fig:graph3),
where the vast majority of respondents report spending a considerable amount
of real world currencies on purchasing VPs through the pearl shop.
For reference, a 30-day value pack in the pearl shop costs 1500 pearls
(the equivalent of $15.00 USD).

```{r graph3, fig.cap="Spending on VPs in Pearl Shop Versus Number of VPs Purchased on Central Market", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Row 60 is potential outlier; may have purchased lots of VPs in order to sell
#   them on the central market for silver
cleaned_data[-c(6,24,60,112),] |>
  ggplot(aes(x = ps_vp_usd, y = cm_vp_count)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  theme_minimal() +
  labs(x = "Spending on Value Pack in Pearl Shop (USD)",
       y = "Number of VPs Purchased on Central Market")
```

### Gender of Characters

Gender-based appeal is a deep-rooted design pattern in most Korean MMOs.
(`FIND SOME SOURCE FOR THIS SHIT`)
Most cosmetic options are designed to appeal to the general playerbase and often
forfeits any semblance of practicality. This issue is very apparent in female
armor designs in Korean MMOs, and Black Desert Online is generally not an
exception to this. To see if these appeal-based design decisions truly have
any merit behind them, data was collected on the number of adult
female characters that each respondent has. The intent is to compare it with
their spending in cosmetic items, as briefly demonstrated in
Figure \@ref(fig:graph4).

```{r graph4, fig.cap="Number of female characters Versus Total Spending", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Create a scatterplot on number of female characters versus total spending
cleaned_data |>
  ggplot(aes(x = character_female, y = ps_cosmetic_usd)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  theme_minimal() +
  labs(x = "Spending on Value Pack in Pearl Shop (USD)",
       y = "Number of VPs Purchased on Central Market")
```

@@

\begin{equation}
Y_i = \beta_0 + \beta_1 X_i + \beta_2 X_i (\#eq:linm)
\end{equation}

The general assumption behind the consideration of this model is that
as a player spends more time in BDO, the more likely they are to spend more
real world currencies in exchange for in-game items. This could be due to their
need to continue using subscription-esque items that grant them boosts, or
due to the creation of more content in the game that requires real world
currencies to purchase (such as cosmetic items). Given the context of 
gender-based appeal in Korean MMOs such as BDO, there could also be a connection
between number of female characters and a player's spending in the pearl shop.
The null hypothesis of this model therefore seeks to explore whether there 
really is a statistically significant connection between the total amount
of money spent in-game and the factors mentioned above. 
Equivalently,

\begin{equation}
H_0: \beta_1, \beta_2 \neq 0
\end{equation}

Equation \@ref(eq:linm) represents the model used in this paper, where
$Y_i$, the dependent variable, is a player's total spending in pearl shop,
$\beta_0$ is the intercept, $\beta_1$ is the covariate of total playtime,
$\beta_2$ is the covariate of number of female characters the player has.

Since the dependent variable is continuous, a linear model is considered instead
of a logistic model. For the analysis in the rest of this section, the dataset
is split 80%/20% for training/testing purposes. The statistical programming 
language `R` [@citeR] is used to run this model and present the findings from
it.

@@

TODO; Concrete findings accompanied by graphs

@@

TODO; speculations as to why we saw a particular trend, its implications.
Limitations. Further Directions.
